Binarity's Biases on Transit Survey Occurrence Rates

### 2018-02-28 paper/main.tex
text: minor

From within this sample of apparently searchable sources, the
observers sum the number of detections ${\rm d}N_{\rm det}$ of planets
with an apparent radius between $r\a$ and $r\a + dr\a$.  There will be
three contributions to this sum,
\begin{align}
  {\rm d}N_{{\rm det},0} &= 
      \frac{N_\star(r\a) p_{\rm tra}}{1+\mu}
      \Gamma_0(r\a)\mathrm{d}r\a,
  \label{eq:n0} \\
  {\rm d}N_{{\rm det},1} &= 
      \frac{\mu N_\star(r\a) p_{\rm tra}}{1+\mu} 
      \Gamma_1(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
	\label{eq:n1} \\
  {\rm d}N_{{\rm det},2} &=
      \frac{\mu N_\star(r\a) p_{\rm tra}}{1+\mu} 
      \Gamma_2(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a).
	\label{eq:n2}
\end{align}
where here and elsewhere, the subscript 0 refers to single stars, 1
refers to primary stars of binaries, and 2 refers to secondary stars
of binaries. The apparent occurrence rate density is therefore
\begin{equation}
  \Gamma\a(r\a) = \frac{{\rm d}N_{\rm det}}{{\rm d}r\a} \frac{1}{N_\star(r\a) p_{\rm tra}} =
  \frac{\Gamma_0(r\a)}{1+\mu} +
  \frac{\mu\sqrt{2}\,\Gamma_1(\sqrt{2}r\a)}{1+\mu} +
  \frac{\mu\sqrt{2}\,\Gamma_2(\sqrt{2}r\a)}{1+\mu}.
	\label{eq:formula_twin_binary}
\end{equation}
Our earlier results, Equations~\ref{eq:rate_at_rp}
and~\ref{eq:correction_diluted_rp}, are recovered by integrating this
formula over $r$ after inserting
\begin{equation}
  \Gamma_i(r) = \Lambda_{r\p}\, \hat{\delta}(r-r\p),~~{\rm for}\ i\in\{0,1,2\}
\end{equation}
where $\hat{\delta}$ is the Dirac delta function, and $\Lambda_{r\p}$
is the number of planets with size $r\p$ per star considered in
Section~\ref{sec:model_1}.

@@

For planets smaller than 2\,$R_\oplus$, the true occurrence rate
density is more uncertain because such planets are more difficult to
detect.  To investigate the systematic errors associated with binarity
on the inferred occurrence rate of Earth-sized planets, we need to
make plausible assumptions about the true occurrence rate density.
Obviously if the rate density continues to vary as $r^{-3}$ down to
much smaller planet sizes, the results of the preceding section will
hold.  But there is no particular reason to think this will be the
case and indeed, some investigators have concluded that the rate
density begins to level off to a constant value as $r$ decreases below
$2R_\oplus$~\citep{petigura_plateau_2013}.  To investigate the
implications we consider a broken power-law:
\begin{align}
    f(r)
    &\propto
    \left.
    \begin{cases}
        r^\gamma & \text{for } r\geq 2R_\oplus \\
        {\rm constant} & \text{for } r\leq2R_\oplus.
    \end{cases}
    \right.
    \label{eq:model3_radius_distribution}
\end{align}
In this case the integrals that appear in
Equation~\ref{eq:general_Gamma_a} are tedious to work out
analytically, leading us to evaluate them numerically.\footnote{We
refer the interested reader to our online code for performing this
computation: \url{github.com/lgbouma/binary_biases}, commit
\texttt{4e517fe}.} Figure~\ref{fig:occ_rate_model_3_log} shows the
results, again for the case $n\b/n\s=0.79$, $\alpha = 3.5$, $\beta=0$,
and $\gamma=-2.92$.

>>>>

From within this sample of apparently searchable sources, the
observers sum the number of detections ${\rm d}N_{\rm det}$ of planets
with an apparent radius between $r\a$ and $r\a + dr\a$.  There will be
three contributions to this sum,
\begin{align}
  {\rm d}N_{{\rm det},0} &= 
      \frac{N_\star(r\a) p_{\rm tra}}{1+\mu}
      \Gamma_0(r\a)\mathrm{d}r\a,
  \label{eq:n0} \\
  {\rm d}N_{{\rm det},1} &= 
      \frac{\mu N_\star(r\a) p_{\rm tra}}{1+\mu} 
      \Gamma_1(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
	\label{eq:n1} \\
  {\rm d}N_{{\rm det},2} &=
      \frac{\mu N_\star(r\a) p_{\rm tra}}{1+\mu} 
      \Gamma_2(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a).
	\label{eq:n2}
\end{align}
where here and elsewhere, the subscript 0 refers to single stars, 1
refers to primary stars of binaries, and 2 refers to secondary stars
of binaries. The apparent occurrence rate density is therefore
\begin{equation}
  \Gamma\a(r\a) = \frac{{\rm d}N_{\rm det}}{{\rm d}r\a} \frac{1}{N_\star(r\a) p_{\rm tra}} =
  \frac{\Gamma_0(r\a)}{1+\mu} +
  \frac{\mu\sqrt{2}\,\Gamma_1(\sqrt{2}r\a)}{1+\mu} +
  \frac{\mu\sqrt{2}\,\Gamma_2(\sqrt{2}r\a)}{1+\mu}.
	\label{eq:formula_twin_binary}
\end{equation}
Our earlier results, Equations~\ref{eq:rate_at_rp}
and~\ref{eq:correction_diluted_rp}, are recovered by integrating this
formula over $r$ after inserting
\begin{equation}
  \Gamma_i(r) = \Lambda_{r\p}\, \hat{\delta}(r-r\p),~~{\rm for}\ i\in\{0,1,2\}
\end{equation}
where $\hat{\delta}$ is the Dirac delta function, and $\Lambda_{r\p}$
is the number of planets per star with size $r\p$ considered in
Section~\ref{sec:model_1}.

@@

For planets smaller than 2\,$R_\oplus$, the true occurrence rate
density is more uncertain because such planets are more difficult to
detect.  To investigate the systematic errors associated with binarity
on the inferred occurrence rate of Earth-sized planets, we need to
make plausible assumptions about the true occurrence rate density.
Obviously if the rate density continues to vary as $r^{-3}$ down to
much smaller planet sizes, the results of the preceding section will
hold.  But there is no particular reason to think this will be the
case and indeed, some investigators have concluded that the rate
density begins to level off to a constant value as $r$ decreases below
$2R_\oplus$~\citep{petigura_plateau_2013}.  To investigate the
implications we consider a broken power-law:
\begin{align}
    f(r)
    &\propto
    \left.
    \begin{cases}
        r^\gamma & \text{for } r\geq 2R_\oplus \\
        {\rm constant} & \text{for } r\leq2R_\oplus.
    \end{cases}
    \right.
    \label{eq:model3_radius_distribution}
\end{align}
In this case the integrals that appear in
Equation~\ref{eq:general_Gamma_a} are tedious to work out
analytically, leading us to evaluate them numerically.\footnote{We
refer the interested reader to our online code for performing this
computation: \url{github.com/lgbouma/binary_biases}, commit
\texttt{74fe7e4}.} Figure~\ref{fig:occ_rate_model_3_log} shows the
results, again for the case $n\b/n\s=0.79$, $\alpha = 3.5$, $\beta=0$,
and $\gamma=-2.92$.
